Speeding up decimal multiplication

### 2020-11-25 paper/paper.tex
Update

@@

IDFT of length $N = RC$ can be computed as follows, not counting final multiplication by $N^{-1}$:
\begin{enumerate}
    \item $[C \times R],$ transpose the matrix.
    \item $[R \times C],$ perform (length $C$) IDFT on each row with $\xi = (\xi_N)^R.$
    \item $[R \times C],$ multiply each element indexed $\langle i,j \rangle$ by $(\xi_N)^{-ij}.$
    \item $[R \times C],$ perform (length $R$) IDFT on each column with $\xi = (\xi_N)^C.$
\end{enumerate}

@@

IDFT of length $N = RC$ can be computed as follows, not counting final multiplication by $N^{-1}$:
\begin{enumerate}
    \item $[C \times R],$ transpose the matrix.
    \item $[R \times C],$ perform (length $C$) IDFT on each row with $\xi = (\xi_N)^R.$
    \item $[R \times C],$ multiply each element indexed $\langle i,j \rangle$ by $(\xi_N)^{-ij}.$
    \item $[R \times C],$ transpose the matrix.
    \item $[C \times R],$ perform (length $R$) IDFT on each row with $\xi = (\xi_N)^C.$
    \item $[C \times R],$ transpose the matrix.
\end{enumerate}

@@

Remember in section~\ref{section:omitting1} we established~\eqref{eq:cdot_permutation_invariance}.
We then used this property to get rid of bit-reversal permutations in DIT and DIF.
It turns out that, for both four-step and six-step algorithms,
the same property can be employed to get rid of the
final transposition step in DFT and the initial transposition step in IDFT simultaneously.

@@

Observe that steps 1 and 2 of the direct transform:
\begin{itemize}
\item length-3 DFT on each column,
\item multiplication by $(\xi_N)^{ij},$
\end{itemize}
as well as steps 3 and 4 of the inverse transform:
\begin{itemize}
\item multiplication by $(\xi_N)^{-ij},$
\item length-3 IDFT on each column,
\end{itemize}
can be merged --- performed in a single pass over the columns.
In fact, they \textit{should} be merged, as it produces less loads/stores and leads to better
cache utilization.

@@

Consider now the case of inverse transform.
We need to multiply each matrix element indexed $\langle i,j \rangle$
by $(\xi_N)^{-ij},$ then perform length-3 IDFT on each column; and also multiply everything by a
factor $\Phi.$

>>>>

    \item IDFT* means IDFT without multiplication by $N^{-1}.$

@@

IDFT* of length $N = RC$ can be computed as follows:
\begin{enumerate}
    \item $[C \times R],$ transpose the matrix.
    \item $[R \times C],$ perform (length $C$) IDFT* on each row with $\xi = (\xi_N)^R.$
    \item $[R \times C],$ multiply each element indexed $\langle i,j \rangle$ by $(\xi_N)^{-ij}.$
    \item $[R \times C],$ perform (length $R$) IDFT* on each column with $\xi = (\xi_N)^C.$
\end{enumerate}

@@

IDFT* of length $N = RC$ can be computed as follows:
\begin{enumerate}
    \item $[C \times R],$ transpose the matrix.
    \item $[R \times C],$ perform (length $C$) IDFT* on each row with $\xi = (\xi_N)^R.$
    \item $[R \times C],$ multiply each element indexed $\langle i,j \rangle$ by $(\xi_N)^{-ij}.$
    \item $[R \times C],$ transpose the matrix.
    \item $[C \times R],$ perform (length $R$) IDFT* on each row with $\xi = (\xi_N)^C.$
    \item $[C \times R],$ transpose the matrix.
\end{enumerate}

@@

Remember in section~\ref{section:omitting1} we established~\eqref{eq:cdot_permutation_invariance}.
We then used this property to get rid of bit-reversal permutations in DIT and DIF.
It turns out that, for both four-step and six-step algorithms,
the same property can be employed to get rid of the
final transposition step in DFT and the initial transposition step in IDFT* simultaneously.

@@

Observe that steps 1 and 2 of the direct transform:
\begin{itemize}
\item length-3 DFT on each column,
\item multiplication by $(\xi_N)^{ij},$
\end{itemize}
as well as steps 3 and 4 of the inverse transform:
\begin{itemize}
\item multiplication by $(\xi_N)^{-ij},$
\item length-3 IDFT* on each column,
\end{itemize}
can be merged --- performed in a single pass over the columns.
In fact, they \textit{should} be merged, as it produces less loads/stores and leads to better
cache utilization.

@@

Consider now the case of inverse transform.
We need to multiply each matrix element indexed $\langle i,j \rangle$
by $(\xi_N)^{-ij},$ then perform length-3 IDFT* on each column; and also multiply everything by a
factor $\Phi.$
